### 2018-07-11 Sections/quality_of_service.tex
mdframed
Ent purif

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a dephasing error model in this instance, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} = F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1,	
\end{align}
which corresponds to a bit-flip error model (Sec.~\ref{sec:dephasing_error}). Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing Bell projections (Sec.~\ref{sec:bell_proj}) on their two qubits, classically communicating their measurement outcomes, and performing appropriate local corrections. This is best illustrated by example.

For this model, we will assume our Bell projections destroy the first of their two input qubits, while the second one remains as the output. Then two such projections project a four-qubit state down to a two-qubit state as desired.

Suppose there was no error. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}\bra{\Phi^+} \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon inspection it is evident that if a Bell projection between Alice's two qubits (1 and 3) yields the $\ket{\Phi^+}$ outcome, Bob's projection (2 and 4) must also yield $\ket{\Phi^+}$. Similarly, whatever Bell outcome Alice measures, Bob will measure the same outcome. Upon classically communicating that they measured consistent outcomes, they are satisfied the final state is error-free, and it is.

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the Bell measurements as before, suppose Alice measures the $\ket{\Psi^+}$ outcome. Now Bob must measure the $\ket{\Phi^+}$ outcome, and a comparison of measurement outcomes diagnoses this single bit-flip error, which may subsequently be corrected with an additional bit-flip.

In the above two scenarios (no error, or exactly one error), the state is correctable to a perfect Bell pair. What if there are two errors? Consider the input state with bit-flips affecting both Bell pairs. Then,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \hat{X}_3\ket{\Phi^+}\bra{\Phi^+}\hat{X}_3\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the Bell projections, both Alice and Bob are guaranteed to measure the same outcome, as per the error-free case. However this isn't error-free at all since the remaining state is $\ket{\Psi^+}$ not $\ket{\Phi^+}$. That is, the bit-flip error has permeated through to the corrected state.

@@

Similar reasoning as above can be employed to correct against phase-flip errors, and depolarising errors more generally.

@@

\begin{table}[!htb]
\fbox{\parbox{0.965\columnwidth}{\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\text{CNOT}}_{1,2}\hat{\text{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
}}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}

>>>>

More concretely, we distribute two Bell pairs of fidelity $F$ between Alice and Bob. Let us assume a dephasing error model in this instance, in which case the imperfect Bell pairs are of the form,
\begin{align}
\hat\rho^F_{A,B} = F\ket{\Phi^+}\bra{\Phi^+} + (1-F)\hat{X}_1\ket{\Phi^+}\bra{\Phi^+}\hat{X}_1,	
\end{align}
which corresponds to a bit-flip error model (Sec.~\ref{sec:dephasing_error}). That is, we have a mixture of,
\begin{align}
\ket{\Phi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{0}_B + \ket{1}_A\ket{1}_B),	
\end{align}
with probability $F$, and,
\begin{align}
\ket{\Psi^+} = \frac{1}{\sqrt{2}}(\ket{0}_A\ket{1}_B + \ket{1}_A\ket{0}_B),	
\end{align}
with probability \mbox{$1-F$}. The goal is to `filter' out the latter of these.

Alice and Bob then perform their entanglement purification protocol -- operations to reduce them to a single Bell pair of higher fidelity,
\begin{align}
\mathcal{E}_\text{purif}(\hat\rho^{F_\text{in}}_{A,B} \otimes \hat\rho^{F_\text{in}}_{A,B}) \to \hat\rho^{F_\text{out}}_{A,B},
\end{align}
where,
\begin{align}
F_\text{out}>F_\text{in}.
\end{align}

The purification process $\mathcal{E}_\text{purif}$ is realised very simply by Alice and Bob both performing parity measurements\index{Bell measurement} (see Sec.~\ref{sec:bell_proj} for an optical implementation) on their two qubits, whose measurement outcomes indicate whether two qubits were equal ($+$) or different ($-$). These are easily implemented using CNOT gates, using the construction shown in Fig.~\ref{fig:parity_meas}. They complete the protocol by classically communicating their measurement outcomes, and performing appropriate local corrections. This is best illustrated by example.

\begin{figure}[!htb]
	\begin{align}
		\Qcircuit @C=.7em @R=.4em @! {
		\lstick{} & \qw & \targ & \meter \\
		\lstick{} & \qw & \ctrl{-1} & \qw
		} \nonumber
	\end{align}
	\caption{Construction of a parity measurement circuit using a single CNOT gate and a single-qubit measurement. The measurement outcome indicates whether the two input qubits were the same (\mbox{$\ket{0}\ket{0}$}, \mbox{$\ket{1}\ket{1}$}) or different (\mbox{$\ket{0}\ket{1}$}, \mbox{$\ket{1}\ket{0}$}).}\label{fig:parity_meas}
\end{figure}

For this model, we will assume our parity projections destroy the first of their two input qubits, while the second one remains as the output. Then two such projections project a 4-qubit state down to a 2-qubit state as desired.

Suppose there was no error. Then the input state was,
\begin{align}
\ket\psi_\text{in} &= \ket{\Phi^+}\bra{\Phi^+} \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{0}_1\ket{0}_2+\ket{1}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Now upon inspection it is evident that if a parity projection between Alice's two qubits (1 and 3) yields the $+$ outcome, Bob's projection (2 and 4) must also yield $+$. Similarly, for the $-$ outcome. Upon classically communicating that they measured consistent outcomes, they are satisfied the final state is error-free, and it is, leaving them with a perfect $\ket{\Phi^+}$ state.

Now suppose there was a bit-flip error on the first qubit of the first pair. Now the input state is,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \ket{\Phi^+}\bra{\Phi^+}\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{0}_3\ket{0}_4+\ket{1}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurements as before, suppose Alice measures the $+$ outcome. Now Bob must measure the $-$ outcome, and a comparison of measurement outcomes diagnoses this single bit-flip error, which may subsequently be corrected with an additional bit-flip.

In the above two scenarios (no error, or exactly one error), the state is correctable to a perfect Bell pair. What if there are two errors? Consider the input state with bit-flips affecting both Bell pairs. Then,
\begin{align}
\ket\psi_\text{in} &= \hat{X}_1 \ket{\Phi^+}\bra{\Phi^+}\hat{X}_1 \otimes \hat{X}_3\ket{\Phi^+}\bra{\Phi^+}\hat{X}_3\\
&= \frac{1}{2}(\ket{1}_1\ket{0}_2+\ket{0}_1\ket{1}_2)(\ket{1}_3\ket{0}_4+\ket{0}_3\ket{1}_4).\nonumber
\end{align}
Upon performing the parity measurement, both Alice and Bob are guaranteed to measure the same outcome, as per the error-free case. However this isn't error-free at all since the remaining state is $\ket{\Psi^+}$ not $\ket{\Phi^+}$. That is, the bit-flip error has permeated through to the `corrected' state.

@@

The full circuit for this entanglement purification protocol is shown in Fig.~\ref{fig:ent_purif_circ}.

\begin{figure}[!htb]
\includegraphics[width=0.39\textwidth]{entanglement_purification}
\caption{Protocol for entanglement purification of two noisy Bell-pairs (blue) into a single less noisy Bell-pair. Not shown are trivial single-qubit local corrections that may need to be made, depending upon measurement outcomes.} \label{fig:ent_purif_circ}
\end{figure}

Similar reasoning as above can be employed to correct against phase-flip errors by operating in a Hadamard-rotated basis.

@@

\begin{table}[!htb]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function ThreeQubitCode($\ket\psi$):
\begin{enumerate}
\item Using two CNOT gates, redundantly encode the logical single-qubit state,
\begin{align}
\ket\psi=\alpha\ket{0}+\beta\ket{1},
\end{align}
into the 3-qubit state,
\begin{align}
\ket\psi_R &= \hat{\text{CNOT}}_{1,2}\hat{\text{CNOT}}_{1,3}\ket\psi\ket{00} \nonumber \\
&= \alpha\ket{000}+\beta\ket{111}.
\end{align}
\item Independently apply bit-flip channels $\mathcal{E}_X$ to each of the three encoded qubits.
\item If exactly one bit-flip operation was applied in total, the three possible erroneous encoded states are,
\begin{align}
\ket\psi_1 &= \hat{X}_1 \ket\psi_R = \alpha\ket{001}+\beta\ket{110}, \nonumber \\
\ket\psi_2 &= \hat{X}_2 \ket\psi_R = \alpha\ket{010}+\beta\ket{101}, \nonumber \\
\ket\psi_3 &= \hat{X}_3 \ket\psi_R = \alpha\ket{100}+\beta\ket{011}.
\end{align}
\item Determine the parity of each of the three pairs of encoded qubits.
\item Assuming at most a single bit-flip operation has occurred on the encoded state, the three parity outcomes uniquely determine which encoded qubit the bit-flip was applied to.
\item Apply classically-controlled bit-flip recovery operations, $\mathcal{R}$, to correct the encoded state, recovering $\ket\psi_R$.
\item Apply the inverse of the encoding operation to recover $\ket\psi$.
\item $\Box$
\end{enumerate}}
\begin{align}
\Qcircuit @C=1.3em @R=.6em {
  & \lstick{\ket{\psi}} & \ctrl{2} & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{3}  & \qw       & \ctrl{4} & \qw & \multigate{2}{\ \mathcal{R}\ } & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \ctrl{2}  & \ctrl{2}  & \qw      & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  & \lstick{\ket{0}}    & \targ    & \gate{\mathcal{E}_X}  & \qw & \qw              & \qw       & \ctrl{2}  & \ctrl{3} & \qw & \ghost{\ \mathcal{R}\ } \qw & \qw \\
  &          &          &          & & \lstick{\ket{0}} & \targ \qw & \qw       & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \targ \qw & \qw      & \meter & \control \cw \cwx \\
  &          &          &          & & \lstick{\ket{0}} & \qw       & \qw       & \targ    & \meter & \control \cw \cwx
} \nonumber
\end{align}
\end{mdframed}
\caption{3-qubit code for protecting against at most a single logical bit-flip error. The doubly-controlled CNOT gates represent parity measurements, \mbox{$n_3=n_1\oplus n_2$}, where $n_i$ represents the value of the $i$th qubit. In a Hadamard-rotated basis, the same circuit may be employed to protect against a single phase-flip error. And by concatenating the two we obtain a 9-qubit code protecting against a single depolarising error (i.e joint bit-flip/phase-flip), which is a universal single-qubit error model.} \label{alg:three_QEC}
\end{table}
